---
title: "Single Dataframe Operations"
author: "R package build"
date: '2022-02-15'
slug: single-dataframe-operations
categories: []
tags: []
---

```{r}
library(tidyverse)
```

```{r}
url <- 'https://github.com/Lior1430/tidyverse/blob/main/hotels.csv?raw=true'
hotels <- read_csv(url)
names(hotels)
```

## Selecting Variables

### Select to Keep Variables
```{r}
hotels %>% 
  select(hotel, lead_time)
```

### Select to Exlude Variables
```{r}
hotels %>%
  select(-agent)
```
### Select a Range of Variables
```{r}
hotels %>%
  select(hotel:arrival_date_month)
```
### Select Variables with Characteristics
```{r}
hotels %>% 
  select(ends_with("type"))
```
```{r}
hotels %>% 
  select(starts_with("arrival"))
```
## Arranging Variables

### Arranging in Ascending
```{r}
hotels %>%
  select(adults, children, babies) %>% 
  arrange(babies)
```
### Arranging in Descending Order
```{r}
hotels %>% 
  select(adults, children, babies) %>%
  arrange(desc(babies))
```
## Slicing Variables

### Slicing for Certain Row Numbers
```{r}
# first five
hotels %>%
  slice(1:5)
```

## Filtering Variables

### Filter to Select Subset of Rows
```{r}
# bookings in City Hotels
hotels %>% 
  filter(hotel == "City Hotel")
```

### Filter for Many Conditions
```{r}
hotels %>% 
  filter(
    adults == 0,
    children >= 1
  ) %>%
  select(adults, babies, children)
```

### Filter for Complex Conditions
```{r}
# bookings with no adults and some children or babies in the room
hotels %>% 
  filter(
    adults == 0, 
    children >= 1 | babies >= 1 
  ) %>%
  select(adults, babies, children)
```
## Distinct and Count

### Distinct to Filter for Unique Rows
```{r}
hotels %>%
  distinct(market_segment) %>% 
  arrange(market_segment)
```

```{r}
hotels %>%
  distinct(hotel, market_segment) %>%
  arrange(hotel, market_segment)
```

### Count to Create Frequency Tables
```{r}
hotels %>% 
  count(market_segment)
```

```{r}
hotels %>% 
  count(market_segment, sort = TRUE)
```

### Count and Arrange
```{r}
hotels %>% 
  count(market_segment) %>% 
  arrange(n)
```
```{r}
hotels %>% 
  count(market_segment) %>% 
  arrange(desc(n))
```

### Count for Multiple Variables
```{r}
hotels %>%
  count(hotel, market_segment)
```

## Mutating Variables

### Mutate to Add a New Variable
```{r}
hotels %>%
  mutate(little_ones = children + babies)  %>%
  select(children, babies, little_ones) %>%
  arrange(desc(little_ones))
```

## summarise and group_by

### Summarise for Summary Stats
```{r}
hotels %>%
  summarise(mean_adr = mean(adr))
```

### Group_by for Grouped Operations
```{r}
hotels %>% 
  group_by(hotel) %>%
  summarise(mean_adr = mean(adr))
```

