---
title: "Data Classes"
author: "R package build"
date: '2022-02-23'
slug: data-classes
categories: []
tags: []
---

# Data Classes

```{r}
library(tidyverse)
```

## Factors
```{r}
x <- factor(c("BS", "MS", "PhD", "MS"))
x
```
```{r}
typeof(x)

class(x)
```

### Factors Have Level Labels and Level Numbers
```{r}
glimpse(x)
```

```{r}
as.integer(x)
```

## Dates
```{r}
y <- as.Date("2022-02-23")
y
```
```{r}
typeof(y)

class(y)
```

### Dates Are Two Integers Glued Together
```{r}
#number of days since the origin and the origin (1 Jan 1970)
as.integer(y)
```

#### Calculate How Many Years
```{r}
as.integer(y) / 365
```

## Data Frames
```{r}
df <- data.frame(x = 1:2, y = 3:4)
df
```
```{r}
typeof(df)

class(df)
```

### Lists
```{r}
l <- list(
  x = 1:4,
  y = c("hi", "hello", "jello"),
  z = c(TRUE, FALSE)
)
l
```

### Extract a Vector from a Data Frame
```{r}
df %>%
  pull(y)
```

# Working with Factors

## Call Libraries
```{r}
library(tidyverse)
catlovers <- "https://raw.githubusercontent.com/Lior1430/tidyverse/main/cat-lovers.csv"

cat_lovers <- read_csv(catlovers)
```

## Read Data
```{r}
glimpse(cat_lovers)
```

## Plot the Data
```{r}
ggplot(cat_lovers, mapping = aes(x = handedness)) +
  geom_bar()
```

### Change Factors
```{r}
cat_lovers %>%
  mutate(handedness = fct_infreq(handedness)) %>%
  ggplot(mapping = aes(x = handedness)) +
  geom_bar()
```

# Working with Dates

## Call Libraries
```{r}
library(tidyverse)
library(lubridate)
hotel <- "https://raw.githubusercontent.com/Lior1430/tidyverse/main/hotels.csv"

hotels <- read_csv(hotel)
```

## Calculate and Visualize Number of Bookings on any Arrival Date
```{r}
hotels %>%
  select(starts_with("arrival_"))
```

### Step 1: Construct Dates
```{r}
library(glue)

hotels %>%
  mutate(
    arrival_date = ymd(glue("{arrival_date_year} {arrival_date_month} {arrival_date_day_of_month}"))
    ) %>% 
  relocate(arrival_date)
```

### Step 2: Count Bookings per Date
```{r}
hotels %>%
  mutate(arrival_date = ymd(glue("{arrival_date_year} {arrival_date_month} {arrival_date_day_of_month}"))) %>% 
  count(arrival_date)
```

### Visualize Bookings per Date
```{r}
hotels %>%
  mutate(arrival_date = ymd(glue("{arrival_date_year} {arrival_date_month} {arrival_date_day_of_month}"))) %>% 
  count(arrival_date) %>%
  ggplot(aes(x = arrival_date, y = n, group = 1)) +
  geom_line()
```

#### Visualize Using a Smooth Curve
```{r}
hotels %>%
  mutate(arrival_date = ymd(glue("{arrival_date_year} {arrival_date_month} {arrival_date_day_of_month}"))) %>% 
  count(arrival_date) %>%
  ggplot(aes(x = arrival_date, y = n, group = 1)) +
  geom_smooth()
```

