---
title: Data IO
author: R package build
date: '2022-02-23'
slug: data-io
categories: []
tags: []
---

# Importing Data

## Reading Rectangular Data into R
```{r}
library(tidyverse)
library(readr)
library(readxl)
```

## Reading Data into R
```{r}
nobel <- read_csv(file = "https://github.com/Lior1430/tidyverse/blob/main/nobel.csv")
nobel
```

## Writing Data
```{r}
df <- tribble(
  ~x, ~y,
  1,  "a",
  2,  "b",
  3,  "c"
)
write_csv(df, file = "df.csv")
```

```{r}
read_csv("df.csv")
```

# Variable Names

## Data with Bad Names
```{r}
edibnb_badnames <- read_csv("https://github.com/Lior1430/tidyverse/raw/main/edibnb-badnames.csv")
names(edibnb_badnames)
```

### Option 1: Define Column Names
```{r}
edibnb_col_names <- read_csv("https://github.com/Lior1430/tidyverse/raw/main/edibnb-badnames.csv",
                             col_names = c("id", "price", 
                                           "neighbourhood", "accommodates",
                                           "bathroom", "bedroom", 
                                           "bed", "review_scores_rating", 
                                           "n_reviews", "url"))
names(edibnb_col_names)
```

### Option 2: Format Text to snake_case
```{r}
edibnb_clean_names <- read_csv("https://github.com/Lior1430/tidyverse/raw/main/edibnb-badnames.csv") %>%
  janitor::clean_names()
names(edibnb_clean_names)
```

# Variable Types
```{r}
read_csv("https://github.com/Lior1430/tidyverse/raw/main/df-na.csv")
```
## Option 1: Explicit NA's
```{r}
read_csv("https://github.com/Lior1430/tidyverse/raw/main/df-na.csv", 
         na = c("", "NA", ".", "9999", "Not applicable"))
```

## Option 2: Specify Column Types
```{r}
read_csv("https://github.com/Lior1430/tidyverse/raw/main/df-na.csv", col_types = list(col_double(), 
                                            col_character(), 
                                            col_character()))
```

# Favorite Foods
```{r}
library(readxl)
fav_food <- read_excel("~/Downloads/favourite-food.xlsx")
fav_food
```

## Variable Names
```{r}
fav_food <- read_excel("~/Downloads/favourite-food.xlsx") %>%
  janitor::clean_names()
fav_food

```

## Handling NA's
```{r}
fav_food <- read_excel("~/Downloads/favourite-food.xlsx",
                       na = c("N/A", "99999")) %>%
  janitor::clean_names()
fav_food
```

## Make Age Numeric
```{r}
fav_food <- fav_food %>%
  mutate(
    age = if_else(age == "five", "5", age),
    age = as.numeric(age)
    )
glimpse(fav_food)
```

## Socio-economic Status
```{r}
fav_food %>%
  count(ses)
```

## Make ses a Factor
```{r}
fav_food <- fav_food %>%
  mutate(ses = fct_relevel(ses, "Low", "Middle", "High"))
fav_food %>%
  count(ses)
```

## Put it all Together
```{r}
fav_food <- read_excel("~/Downloads/favourite-food.xlsx", na = c("N/A", "99999")) %>%
  janitor::clean_names() %>%
  mutate(
    age = if_else(age == "five", "5", age), 
    age = as.numeric(age),
    ses = fct_relevel(ses, "Low", "Middle", "High")
  )
fav_food
```

## Out and Back in
```{r}
write_csv(fav_food, file = "fav-food-clean.csv")
fav_food_clean <- read_csv("fav-food-clean.csv")
```

```{r}
fav_food_clean %>%
  count(ses)
```

# RDS Files
```{r}
library(tidyverse)
library(readr)
library(readxl)
```

## Out and Back in Part 2
```{r}
write_rds(fav_food, file = "fav-food-clean.rds")
fav_food_clean <- read_rds("fav-food-clean.rds")
fav_food_clean %>%
  count(ses)
```

 