---
title: "Modeling for Prediction"
author: "R package build"
date: '2022-03-21'
slug: modeling-for-prediction
categories: []
tags: []
---

# Questions
## **What are the advantages and disadvantages of k-fold cross validation relative to the Single Split Validation approach?**

    The single split validation approach only allows for one subset to     fit the model which could lead to an overestimation. K-fold           validation relieves this bias. 

## **What are the advantages and disadvantages of k-fold cross validation relative to LOOCV?**

    LOOCV is unbiased compared to k-fold cross validation because it      uses more of the dataset set. Although it is not biased, it has a     higher variance.

## **What are the pros and cons of Bootstrapping?**
### Pros:
      Easy way to estimate confidence intervals
      Easy way to estimate standard errors
      Low cost

### Cons:
      Undervalues extreme values
      Provides info only about original data set
      Does not correct biases

# Import Data
```{r}
library(readr)
```

```{r}
realestate <- read_csv("https://github.com/Lior1430/Real-Estate-Evaluation/raw/main/Real%20estate%20valuation%20data%20set.csv")
```

# Setup
```{r}
library(ISLR)
library(boot)
```

# Cross Validation of housing_median_age and median_house_value
```{r}
set.seed(1)
head(realestate)
dim(realestate)
train_re <- sample(350, 8)
head(train_re)
```
```{r}
attach(realestate)
lm.fit <- lm(`Y house price of unit area` ~ `X2 house age`, data = realestate, subset = train_re)
lm.fit
```
```{r}
mean((`Y house price of unit area` - predict(lm.fit, realestate))[-train_re]^2)
```
```{r}
plot(`Y house price of unit area`, `X2 house age`)
```
```{r}
lm.fit.poly <- lm(`Y house price of unit area`~poly(`X2 house age`, 2), data = realestate, subset = train_re)
lm.fit.poly
```
```{r}
mean((`Y house price of unit area` - predict(lm.fit.poly, realestate))[-train_re]^2)
```

```{r}
n = 2 
set.seed(n)
train_re <- sample(350, 8)
attach(realestate)
lm.fit <- lm(`Y house price of unit area`~ `X2 house age`, data = realestate, subset = train_re)
lm.fit.poly <- lm(`Y house price of unit area`~poly(`X2 house age`, 2), data = realestate, subset = train_re)
lm.fit.poly
```


# K-cross Validation 
## K = 10 for for Y house price of unit area and X2 house age
```{r}
K = 10
cv.error.10 <- rep(0, 5)
degree <- 1:5
for(d in degree){
  glm.fit <- glm(`Y house price of unit area`~poly(`X2 house age`, d), data = realestate)
  cv.error.10[d] <- cv.glm(realestate, glm.fit, K = K)$delta[1]
}
cv.error.10
```
```{r}
plot(degree, cv.error.10, type = "b")
```
## K = 100 for for Y house price of unit area and X2 house age
```{r}
K = 100
cv.error.100 <- rep(0, 5)
degree <- 1:5
for(d in degree){
  glm.fit <- glm(`Y house price of unit area`~poly(`X2 house age`, d), data = realestate)
  cv.error.100[d] <- cv.glm(realestate, glm.fit, K = K)$delta[1]
}
cv.error.100
```
```{r}
plot(degree, cv.error.100, type = "b")
```
## K = 10 for for Y house price of unit area and X4 number of convenience stores
```{r}
K = 10
cv.error.10 <- rep(0, 5)
degree <- 1:5
for(d in degree){
  glm.fit <- glm(`Y house price of unit area`~poly(`X4 number of convenience stores`, d), data = realestate)
  cv.error.10[d] <- cv.glm(realestate, glm.fit, K = K)$delta[1]
}
cv.error.10
```
```{r}
plot(degree, cv.error.10, type = "b")
```
## K = 100 for Y house price of unit area and X4 number of convenience stores
```{r}
K = 100
cv.error.100 <- rep(0, 5)
degree <- 1:5
for(d in degree){
  glm.fit <- glm(`Y house price of unit area`~poly(`X4 number of convenience stores`, d), data = realestate)
  cv.error.100[d] <- cv.glm(realestate, glm.fit, K = K)$delta[1]
}
cv.error.100
```
```{r}
plot(degree, cv.error.100, type = "b")
```

# Bootsrap Validation 
## Y house price of unit area and X2 house age
```{r}
boot.fn <- function(realestate, index){
  return(coef(lm(`Y house price of unit area`~`X2 house age`, data = realestate, subset = index)))
}
```
```{r}
boot.fn(realestate, 1:350)
```
```{r}
set.seed(1)
boot.fn(realestate, sample(350, 350, replace = T))
```
```{r}
boot.out1 <- boot(realestate, boot.fn, 500)
plot(boot.out1)
```
```{r}
boot.out1.2 <- boot(realestate, boot.fn, 1000)
plot(boot.out1.2)
```

## Y house price of unit area and X4 number of convenience stores
```{r}
boot.fn <- function(realestate, index){
  return(coef(lm(`Y house price of unit area`~`X4 number of convenience stores`, data = realestate, subset = index)))
}
```
```{r}
boot.fn(realestate, 1:350)
```
```{r}
set.seed(1)
boot.fn(realestate, sample(350, 350, replace = T))
```
```{r}
boot.out2 <- boot(realestate, boot.fn, 500)
plot(boot.out2)
```
```{r}
boot.out2 <- boot(realestate, boot.fn, 1000)
plot(boot.out2)
```

